Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-20 article.tex
wording

\title[Connectomics challenge]{Inferring neural networks from imaging using
                               partial correlation and sample weighting}

@@

% Issue : we have data, but need to have to infer the connectome
Cutting edge optical devices (TODO CITE) allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. From those imaging signals, the following inverse problem
is set: inferring the network connectivity from the chemical signals.

>>>>

\title[Connectomics challenge]{Inferring neural networks from fluorescent
                               calcium imaging using partial correlation and
                               sample weighting}

@@

% Issue : we have data, but need to have to infer the connectome
Cutting edge optical devices (TODO CITE) allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. The neuron connectivity network could be inferred
from those neuron activity signals.
